---
title: "Conceptual Questions"
format: html
toc: TRUE
editor_options: 
  chunk_output_type: inline
---
```{r}
library(tidyverse)
```


1. If your working directory is myfolder/homework/, what relative path would you specify to get the file located at myfolder/MyData.csv?

> I would use ../MyData.csv

2. What are the major benefits of using R projects?

> R integrates well with Git, and keeps workflow organized (which helps with reproducibility). Additionally, R is free which makes it much more accessible to students and professionals alike. 

3. What is git and what is github?

> Git is version control software that can track changes made to files. Github is a, online hosting platform for git repositories. 

4. What are the two main differences between a tibble and a data.frame?

> A tibble uses fancy printing that gives information on the number of observations, the columns, a shows only a few rows of data. A tibble also does not coerce down to a vector when you subset to only one column using [. 

5. Rewrite the following nested function call using BaseR’s chaining operator:
```{r}
iris |>
  as_tibble() |>
  select(starts_with("Petal"), Species) |>
  filter(Petal.Length < 1.55) |>
  arrange(Species)
```
